Incentivizing Exploration with Unbiased History

### 2018-11-01 main.tex
2level
3-level proof
Start >3 level proof
update model and greedy
Update 2-level proof
edits
rewriting
GITHUB SUCKS
update 2-level figure
stuff
3level
llevel theorems
brown is the new pink
llevel in intro
Moved concentration and anti-concentration theorem statements to appendix.
Moved Greedy into Warmup, and started revising.
Moved a macro to the main file.
Revised some macro.
Changed some macro.
T_G -> alex's macro
q_a -> \fdpN
fun fact: we now have at most 30 q's in the paper
Acknowledgment for  Bobby

\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{mathrsfs}
\usepackage{float}
% ======    PACKAGES
\usepackage{slivkins-setup,slivkins-theorems}
%\usepackage{amsmath, amsfonts, amssymb, amsthm, amsbsy, amscd, bm, bbm}
\usepackage{amsbsy, amscd, bm, bbm}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[small,bf]{caption}
\setlength{\captionmargin}{30pt}
\usepackage{subcaption}
\captionsetup[sub]{margin=10pt,font=small}
\usepackage{color}
\usepackage{ifthen}
\usepackage{xspace}
\usepackage[noend]{algorithmic}
\usepackage{algorithm}
\usepackage[colorlinks,citecolor={black},urlcolor={black},linkcolor={black}]{hyperref}
\usepackage{url}
\usepackage{tocbibind}
\usepackage{enumerate}
\usepackage{mdframed}
\usepackage{comment}

@@

% a very useful package for edits and comments, from David Kempe (USC)
\usepackage{color-edits}
%\usepackage[suppress]{color-edits}  % use this to suppress the package
\addauthor{as}{red}      % as for Alex
\addauthor{jm}{blue}     % jm for Jieming
\addauthor{ni}{green}     % ni for Nicole
\addauthor{sw}{magenta}     % sw for Steven
% e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{conjecture}[theorem]{Conjecture}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{remark}{Remark}[section]
%\newtheorem{claim}{Claim}[section]
%\newtheorem{example}{Example}[section]

\newcommand{\term}[1]{\ensuremath{\mathtt{#1}}}
\newcommand{\thread}{\term{thread}}

@@

\def\DKL{\textbf{D}_{\term{KL}}}
\def\D{\mathbb{D}}
\def\E{\mathbb{E}}

\def\A{\mathcal{A}}
\def\M{\mathcal{M}}
\def\S{\mathcal{S}}
\def\X{\mathcal{X}}
\def\EX{\term{EX}}
\def\Ds{*}
\def\EE{\mathcal{E}}
\def\varTheta{\bold{\Theta}}
\def\varOmega{\bold{\Omega}}

\def\ALGG{Greedy }
\def\ALGPG{Parallel Greedy }
\def\2LEVEL{Two-level Policy}
\def\Ber{\emph{Ber} }

\def\pmn{\hat{\mu}}
\def\emn{\bar{\mu}}

\title{Bayesian Exploration with Unbiased History}

@@

\section{Social Learning}
\begin{lemma}
\ALGG of $T_c$ rounds pulls each arm w.p. at least $p_c$. 
\end{lemma}

\begin{corollary}
\ALGPG of $c \cdot T_c \cdot \frac{1}{p_c} \cdot \log(1/\delta)$ rounds pulls each at least once w.p. $1-\delta$. \jmcomment{Do we actually need this?}
\end{corollary}

@@

\appendix

\input{posterior}
\end{document}

>>>>

\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{mathrsfs}
\usepackage{float}
% ======    PACKAGES
\usepackage{slivkins-setup,slivkins-theorems}
%\usepackage{amsmath, amsfonts, amssymb, amsthm, amsbsy, amscd, bm, bbm}
%\usepackage{amsbsy,amscd, bm, bbm}
\usepackage{kpfonts}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[small,bf]{caption}
\setlength{\captionmargin}{30pt}
\usepackage{subcaption}
\captionsetup[sub]{margin=10pt,font=small}
\usepackage{color}
\usepackage{ifthen}
\usepackage{xspace}
\usepackage[noend]{algorithmic}
\usepackage{algorithm}
\usepackage[colorlinks,citecolor={black},urlcolor={black},linkcolor={black}]{hyperref}
\usepackage{url}
\usepackage{tocbibind}
\usepackage{enumerate}
\usepackage{mdframed}
\usepackage{comment}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\usepackage{cleveref}

@@

% a very useful package for edits and comments, from David Kempe (USC)
\usepackage{color-edits}
%\usepackage[suppress]{color-edits}  % use this to suppress the package
\addauthor{as}{red}      % as for Alex
\addauthor{jm}{blue}     % jm for Jieming
\addauthor{ni}{magenta}     % ni for Nicole
\addauthor{sw}{brown}     % sw for Steven
% e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \newtheorem{theorem}{Theorem}[section]
% \newtheorem{corollary}[theorem]{Corollary}
% \newtheorem{conjecture}[theorem]{Conjecture}
% \newtheorem{proposition}[theorem]{Proposition}
% \newtheorem{definition}[theorem]{Definition}
% \newtheorem{lemma}[theorem]{Lemma}
% \newtheorem{remark}{Remark}[section]
% \newtheorem{claim}{Claim}[section]
% \newtheorem{example}{Example}[section]

\newcommand{\term}[1]{\ensuremath{\mathtt{#1}}\xspace}
\newcommand{\thread}{\term{thread}}
\newcommand{\ALGG}{full-disclosure path }
\newcommand{\ALGPG}{\term{Parallel Greedy}}

% Alex's notation!
\newcommand{\SubH}[1]{\mathcal{H}_{#1}} % subhistory
\newcommand{\AnonSubH}[1]{H^{\texttt{anon}}_{#1}} % subhistory

% new notation for FDPs (full-disclosure paths)
\newcommand{\fdp}{\term{FDP}}
\newcommand{\fdpL}{L^\fdp_K} % sufficient length of greedy path
\newcommand{\fdpP}{p^\fdp_K} % success prob for greedy path
\newcommand{\fdpN}[1][a]{N^\fdp_{K,#1}} % Exp #pulls for arm $a$ in greedy path of length L_K.

% Greedy notation
\def\GdT{L^\fdp_K} % sufficient length of greedy path
\def\GdP{p^\fdp_K} % success prob for greedy path

\def\2LEVEL{two-level policy}

@@

\def\DKL{\textbf{D}_{\term{KL}}}
\def\D{\mathbb{D}}
\def\E{\mathbb{E}}
\def\reg{\mathrm{Reg}}
\def\A{\mathcal{A}}
\def\M{\mathcal{M}}
\def\S{\mathcal{S}}
\def\X{\mathcal{X}}
\def\EX{\term{EX}}
\def\Ds{*}
\def\EE{\mathcal{E}}
\def\varTheta{\bold{\Theta}}
\def\varOmega{\bold{\Omega}}
\def\cD{\mathcal{D}}
\def\cT{\mathcal{T}}
\def\Ber{\emph{Ber} }

\def\pmn{\hat{\mu}}
\def\emn{\bar{\mu}}
%\def\q_a{\fdpN}
%\def\ell{l}

\title{Incentivizing Exploration with Unbiased History}

@@

%\input{algg}

@@

%l-level in the 10page
\input{llevel-overview}

\bibliographystyle{plain}
\bibliography{bib-abbrv,bib-AGT,bib-bandits,bib-ML,bib-random,bib-slivkins}

\section*{Acknowledgment}
We would like to thank Robert Kleinberg for discussions in the early stage of this project.

\appendix
\input{prelim}
\input{app-warmup}
\input{3levelproofs}
\input{llevel}
\input{posterior}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
